%-------------------------
% Resume in Latex
% Author : Aymane El Maini
% My Version: https://github.com/aymaneelmaini/resume
% Original Template: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  {\Large \textbf{Aymane El Maini}} & {\Large \textbf{Software Engineer}} \\
\end{tabular*}

\vspace{2pt}

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \href{https://github.com/aymaneelmaini}{github.com/aymaneelmaini} &
  \href{mailto:elmainiaymane03@gmail.com}{elmainiaymane03@gmail.com} \\
  \href{https://linkedin.com/in/aymane-el-maini}{linkedin.com/in/aymane-el-maini} &
  Mobile: +212-714-934-362 \\
  Location: Marrakesh, Morocco & \\
\end{tabular*}

%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart

  \resumeSubheading
    {ProgressSoft Corporation}{Jordan (Remote)}
    {Associate Software Engineer}{Nov 2024 -- Present}
    \resumeItemListStart
      \resumeItem{PayHub}
        {Contribute to PayHub, a leading enterprise payment hub in the MENA region, developing and maintaining backend APIs and microservices for global payment processing including SWIFT integrations and Visa transactions.}
      \resumeItem{Financial Services}
        {Build scalable and secure financial services using Java, Kotlin, and Spring Boot following Domain-Driven Design principles for banking and financial institutions.}
    \resumeItemListEnd

  \resumeSubheading
    {Foodeals}{Fez, Morocco}
    {Full Stack Developer Intern}{May 2024 -- Aug 2024}
    \resumeItemListStart
      \resumeItem{Full Stack Development}
        {Developed full-stack applications using Spring Boot for backend and Angular for frontend, implementing RESTful APIs and responsive user interfaces.}
      \resumeItem{DevOps \& Containerization}
        {Containerized applications using Docker and collaborated with cross-functional teams using Git for version control.}
    \resumeItemListEnd

  \resumeSubheading
    {ICF Communication}{Marrakesh, Morocco}
    {Front-end Developer Intern}{Apr 2023 -- Jun 2023}
    \resumeItemListStart
      \resumeItem{Web Development}
        {Built responsive web applications using HTML5, JavaScript, CSS3, and Tailwind CSS with a strong focus on usability and performance.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {YouCode - UM6P}{Safi, Morocco}
    {Software Engineering Diploma}{2023 -- 2025}
  \resumeSubheading
    {Ecotstig}{Marrakesh, Morocco}
    {Software Engineering Studies}{2022 -- 2023}
\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart
  \resumeSubItem{\href{https://github.com/aymaneelmaini/klox}{Klox — Java Interpreter}}
    {Tree-walk interpreter implemented in Kotlin following Crafting Interpreters. Supports variables, control flow, functions, closures, and class-based OOP.}
  \resumeSubItem{\href{https://github.com/aymaneelmaini/clox}{Clox — C Interpreter}}
    {Bytecode compiler and stack-based virtual machine written in C. Covers tokenization, compilation, execution, heap allocation, and garbage collection. Tested using Criterion.}
  \resumeSubItem{\href{https://github.com/aymaneelmaini/linkupp}{LinkUp — Friend Matching Platform}}
    {Spring Boot and Kotlin backend using DDD and functional core imperative shell architecture. PostgreSQL, Docker, GitHub Actions CI/CD, and React Native mobile application. Tested with Kotest}
\resumeSubHeadingListEnd

%-----------SKILLS-----------------
\section{Skills}
\resumeSubHeadingListStart
  \item{
    \textbf{Programming}{: Java, Kotlin, C/C++, Go, TypeScript, JavaScript, PHP}
  }
  \item{
    \textbf{Backend}{: Spring Boot, Spring Data, JPA, Hibernate, Exposed ORM, REST, JEE}
  }
  \item{
    \textbf{Frontend}{: Angular, React, Next.js, HTML5, CSS3, Tailwind CSS}
  }
  \item{
    \textbf{Databases}{: PostgreSQL, Oracle, MSSQL, MySQL, MongoDB, Oracle AQ}
  }
  \item{
    \textbf{Testing}{: JUnit 5, Mockito, Kotest, Criterion, Testcontainers, TDD}
  }
  \item{
    \textbf{DevOps}{: Docker, Kubernetes, GitHub Actions, AWS, GCP, Linux}
  }
  \item{
    \textbf{Architecture}{: DDD, Microservices, Functional Programming, Design Patterns}
  }
\resumeSubHeadingListEnd

%-----------LANGUAGES-----------------
\section{Languages}
\resumeSubHeadingListStart
  \item{
    \textbf{Arabic}{: Native} \quad
    \textbf{English}{: Intermediate} \quad
    \textbf{French}{: Intermediate}
  }
\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
